A pipeline to analyse time-course gene expression data

### 2020-06-24 scripts/manuscript.Rmd
MAINT small edits

keywords: >
    time-course gene expression data, clustering, differential expression,
    workflow
vignette: >
    %\VignetteIndexEntry{A worfklow for low-level analyses of scRNA-seq data}
    %\VignetteEngine{knitr::rmarkdown}
output: BiocWorkflowTools::f1000_article
bibliography: bibliography.bib
---
**EAP**: I don't know that describing normalization as part of our tutorial makes sense.
I've tried to change the text.

@@

# TODO list

- Make clear that it applies to RNASeq and how to call the different functions
    to RNASeq
- Check that clustering can deal with count data.
- Make sure package is compatible bioconductor

@@

```{r all_libraries}
# From CRAN
library(NMF)
library(ggfortify)

@@

The first steps of analysis of gene expression data is always to do
normalization and quality control checks of the data. However, in what follows, we do not show the steps for normalization, as these are specific to the platform (microarray); the code for the normalization can be found in as a supplemental file [@abrams:protocol; @park:evalution].

>>>>

keywords: >
    time-course gene expression data, clustering, differential expression,
    workflow
vignette: >
    %\VignetteIndexEntry{A worfklow for low-level analyses of scRNA-seq data}
    %\VignetteEngine{knitr::rmarkdown}
output: BiocWorkflowTools::f1000_article
bibliography: bibliography.bib
---

@@

@@

```{r all_libraries}
# From github
library(timecoursedata)

# From CRAN
library(NMF)
library(ggfortify)

@@

The first steps of analysis of gene expression data is always to do
normalization and quality control checks of the data. However, in what
follows, we do not show the steps for normalization, as these are specific to
the platform (microarray); the code for the normalization can be found in as a
supplemental file [@abrams:protocol; @park:evaluation].
